Statistics Project

### 2022-12-12 rough_analysis.Rmd
Custom Model Add Prediction csv files

```
## Custom Model 
```{r}
# Change categorical values to numeric
housing2 = housing
housing2$Neighborhood <- as.numeric(factor(housing2$Neighborhood,
                                                        levels = c("Blmngtn", "Blueste", "BrDale"),
                                                        labels = c(2,1,0), ordered = TRUE))
housing2$LotConfig <- as.numeric(factor(housing2$LotConfig,
                                                        levels = c("Inside", "Corner", "CulDSac", "FR2", "FR3"),
                                                        labels = c(4,3,2,1,0), ordered = TRUE))
housing2$ExterQual <- as.numeric(factor(housing2$ExterQual,
                                                        levels = c("Ex", "Gd", "TA", "Fa", "Po"),
                                                        labels = c(4, 3, 2,1,0), ordered = TRUE))
housing2$BsmtQual <- as.numeric(factor(housing2$BsmtQual,
                                                        levels = c("Ex", "Gd", "TA", "Fa", "Po"),
                                                        labels = c(4, 3, 2,1,0), ordered = TRUE))

```
```{r}
# Only look at Normal Sales 
normal_housing = housing 
normal_set = normal_housing %>% select(SaleCondition) %>% filter( SaleCondition == c("Normal"))
normal_housing = normal_housing %>% select_if(is.numeric)
```

```{r}
t2 = subset(transformed_numeric, select = -c(LotFrontage, MasVnrArea, GarageYrBlt, OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath )) 
#removal of largely correlated values to reduce multicollinearity (VIF /approx 1) and actually allow back-elimination to run,
#it wasn't running without a ton of errors without this.

@@

>>>>

```
## Custom Model

```{r}
# Change categorical values to numeric
housing2 = housing
housing2$Neighborhood <- as.numeric(factor(housing2$Neighborhood,
                                                        levels = c("Blmngtn", "Blueste", "BrDale"),
                                                        labels = c(2,1,0), ordered = TRUE))
housing2$LotConfig <- as.numeric(factor(housing2$LotConfig,
                                                        levels = c("Inside", "Corner", "CulDSac", "FR2", "FR3"),
                                                        labels = c(4,3,2,1,0), ordered = TRUE))
housing2$ExterQual <- as.numeric(factor(housing2$ExterQual,
                                                        levels = c("Ex", "Gd", "TA", "Fa", "Po"),
                                                        labels = c(4, 3, 2,1,0), ordered = TRUE))
housing2$BsmtQual <- as.numeric(factor(housing2$BsmtQual,
                                                        levels = c("Ex", "Gd", "TA", "Fa", "Po"),
                                                        labels = c(4, 3, 2,1,0), ordered = TRUE))

```
```{r}
# Only look at Normal Sales 
normal_housing = housing 
normal_set = normal_housing %>% select(SaleCondition) %>% filter( SaleCondition == c("Normal"))
normal_housing = normal_housing %>% select_if(is.numeric)

normal_housing$SalePrice = log(normal_housing$SalePrice)
normal_housing$GrLivArea = log(normal_housing$GrLivArea)

```{r}
t2 = subset(normal_housing, select = -c(LotFrontage, MasVnrArea, GarageYrBlt, OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath )) 
#removal of largely correlated values to reduce multicollinearity (VIF /approx 1) and actually allow back-elimination to run,
#it wasn't running without a ton of errors without this.

@@

#-------------------------------------------- Custom Model Prediction:

# Backwards Elimination
test_housing$GrLivArea = log(test_housing$GrLivArea)
back_pred2 = predict(backt2$model, test_housing) 
head(back_pred2)
#Since the original dataset was transformed, we need to counter-transform to reobtain the
#untransformed data.

real_bp2 = exp(back_pred2)

real_bp_joined2 = data.frame(test_housing$Id, real_bp2)
colnames(real_bp_joined2) = c("Id", "SalePrice")
real_bp_joined2[is.na(real_bp_joined2)]<-10000 #if there are any NA, set them to arbitrary 10k price.

head(real_bp_joined2)
write.csv(real_bp_joined2, "./Kaggle_backt2_testset.csv", row.names = FALSE)

# Forward Selection
forward_pred2 = predict(forwardt2$model, test_housing)
real_forward2 = exp(forward_pred2)
real_fp_joined2 = data.frame(test_housing$Id, real_forward2)
real_fp_joined2[is.na(real_fp_joined2)]<-10000
colnames(real_fp_joined2) = c("Id", "SalePrice")
write.csv(real_bp_joined2, "./Kaggle_forwardt2_testset.csv", row.names = FALSE)

# Stepwise Selection 
stepwise_pred2 = predict(stepwiset2$model, test_housing)
real_step2 = exp(stepwise_pred2)
real_sp_joined2 = data.frame(test_housing$Id, real_step2)
real_sp_joined2[is.na(real_sp_joined2)]<-10000
colnames(real_sp_joined2) = c("Id", "SalePrice")
write.csv(real_sp_joined2, "./Kaggle_stepwiset2_testset.csv", row.names = FALSE)
